Interval Probability for Fuzzy Quantum Theories

### 2016-06-19 prob.tex
prob.tex \subsection{Quantum Interval-valued Probability Measures} updates....

% \makeatletter
% \newtheoremstyle{indented}
%   {3pt}% space before
%   {3pt}% space after
%   {\addtolength{\@totalleftmargin}{3.5em}
%    \addtolength{\linewidth}{-3.5em}
%    \parshape 1 3.5em \linewidth}% body font
%   {}% indent
%   {\bfseries}% header font
%   {.}% punctuation
%   {.5em}% after theorem header
%   {}% header specification (empty for default)
% \makeatother
% \theoremstyle{indented}
\theoremstyle{remark}
\newtheorem{example}{Example}
\newtheorem{definition}{Definition}
\newtheorem{cor}{Corollary}
\newtheorem{lemma}{Lemma}
\newcommand{\events}{\ensuremath{\mathcal{E}}}
\newcommand{\qevents}{\ensuremath{\mathcal{E}}}
\newcommand{\pmeas}{\ensuremath{\mu}}
\newcommand{\Hilb}{\mathcal{H}}
\newcommand{\pr}[2]{\langle #1, #2 \rangle}
\newcommand{\ket}[1]{|#1\rangle}
\newcommand{\bra}[1]{\langle#1|}
\newcommand{\ip}[2]{\langle #1 | #2 \rangle}
\newcommand{\proj}[1]{|#1 \rangle\langle #1 |}
\newcommand{\ps}{\texttt{+}}
\newcommand{\ms}{\texttt{-}}
\newcommand{\poss}{{\mbox{\wesa{possible}}}}
\newcommand{\imposs}{{\mbox{\wesa{impossible}}}}
\newcommand{\likely}{{\mbox{\wesa{likely}}}}
\newcommand{\unlikely}{{\mbox{\wesa{unlikely}}}}
\newcommand{\necess}{{\mbox{\wesa{certain}}}}
\newcommand{\overflow}{{\mbox{\wesa{overflow}}}}

@@

\begin{example}[One-qubit quantum probability measure] Consider
a quantum probability measure~$\mu:\events\rightarrow[0,1]$ defined
as follow: 
\[
\mu(E)=\begin{cases}
1 & \textrm{, if }E=\proj{\ps}\textrm{ ;}\\
0 & \textrm{, if }E=\proj{\ms}\textrm{ ;}\\
\mu_{\ket{0}}(E) & \textrm{, otherwise.}
\end{cases}
\]
On one hand, $\mu$ is a probability measure. Because $\mu$ is almost
the same as a probability measure~$\tilde{\mu}_{\ket{0}}$, we only
need to check the orthogonal pair~$\proj{\ps}$ and $\proj{\ms}$:
\[
\mu(\proj{\ps})+\mu(\proj{\ms})=1+0=1\textrm{ .}
\]
On the other hand, $\mu$ cannot be induced by any mixed state because
\[
\mu(\proj{\ps})=\mu(\proj{0})=1\textrm{ .}
\]
However, $\tilde{\mu}_{\rho}(E)=1$ if and only if $\rho$ represents
a pure state and $\rho=E$. \qed\end{example}

@@

>>>>

% \makeatletter
% \newtheoremstyle{indented}
%   {3pt}% space before
%   {3pt}% space after
%   {\addtolength{\@totalleftmargin}{3.5em}
%    \addtolength{\linewidth}{-3.5em}
%    \parshape 1 3.5em \linewidth}% body font
%   {}% indent
%   {\bfseries}% header font
%   {.}% punctuation
%   {.5em}% after theorem header
%   {}% header specification (empty for default)
% \makeatother
% \theoremstyle{indented}
\theoremstyle{remark}
\newtheorem{example}{Example}
\newtheorem{definition}{Definition}
\newtheorem{cor}{Corollary}
\newtheorem{lemma}{Lemma}
\newcommand{\events}{\ensuremath{\mathcal{E}}}
\newcommand{\qevents}{\ensuremath{\mathcal{E}}}
\newcommand{\pmeas}{\ensuremath{\mu}}
\newcommand{\Hilb}{\mathcal{H}}
\newcommand{\pr}[2]{\langle #1, #2 \rangle}
\newcommand{\ket}[1]{|#1\rangle}
\newcommand{\bra}[1]{\langle#1|}
\newcommand{\ip}[2]{\langle #1 | #2 \rangle}
\newcommand{\proj}[1]{|#1 \rangle\langle #1 |}
\newcommand{\ps}{\texttt{+}}
\newcommand{\ms}{\texttt{-}}
\newcommand{\poss}{{\mbox{\wesa{possible}}}}
\newcommand{\imposs}{{\mbox{\wesa{impossible}}}}
\newcommand{\likely}{{\mbox{\wesa{likely}}}}
\newcommand{\unlikely}{{\mbox{\wesa{unlikely}}}}
\newcommand{\necess}{{\mbox{\wesa{certain}}}}
\newcommand{\overflow}{{\mbox{\wesa{overflow}}}}
\newcommand{\unknown}{{\mbox{\wesa{unknown}}}}

@@

\begin{example}[One-qubit quantum probability measure] Consider
a quantum probability measure~$\mu:\events\rightarrow[0,1]$ defined
as follow: 
\[
\mu(E)=\begin{cases}
1 & \textrm{, if }E=\proj{\ps}\textrm{ ;}\\
0 & \textrm{, if }E=\proj{\ms}\textrm{ ;}\\
\tilde{\mu}_{\ket{0}}(E) & \textrm{, otherwise.}
\end{cases}
\]
On one hand, $\mu$ is a probability measure. Because $\mu$ is almost
the same as a probability measure~$\tilde{\mu}_{\ket{0}}$, we only
need to check the orthogonal pair~$\proj{\ps}$ and $\proj{\ms}$:
\[
\mu(\proj{\ps})+\mu(\proj{\ms})=1+0=1\textrm{ .}
\]
On the other hand, $\mu$ cannot be induced by any mixed state because
\[
\mu(\proj{\ps})=\mu(\proj{0})=1\textrm{ .}
\]
However, $\tilde{\mu}_{\rho}(E)=1$ if and only if $\rho$ represents
a pure state and $\rho=E$. \qed\end{example}

@@

\begin{example}[Totally ignorant quantum interval-valued probability
measure] We consider three intervals\emph{ }$\left[0,0\right]$,
$\left[1,1\right]$ and \emph{$\left[0,1\right]$}, where $\left[0,0\right]$
and $\left[1,1\right]$ are called \imposs and \necess as before,
and \emph{$\left[0,1\right]$} is called \unknown because it provides
no information. For any Hilbert space, consider $\mu:\events\rightarrow\mathscr{I}$
defined as follow: 
\[
\mu(E)=\begin{cases}
\necess & \textrm{, if }E=\mathbb{1}\textrm{ ;}\\
\imposs & \textrm{, if }E=\mathbb{0}\textrm{ ;}\\
\unknown & \textrm{, otherwise.}
\end{cases}
\]
It is easy to verify $\mu$ is a quantum interval-valued probability
measure.\qed\end{example}
